Unbiased CVM Algorithm

### 2025-01-06 cvm_unbiased/main.tex
Add counter example

\section{Unbiasedness}
Let $M$ be large enough such that $p^{-1} \leq M$ a.s. (e.g. we can choose $M = f^{-l}$). Then we can derive from Lemma~\ref{le:neg_cor_neg} using $h(x) = x$ and $h(x) = M+1-x$ that:
\begin{eqnarray*}
  \expectation_{\Omega_l} [ p^{-1} I(s \in S) ] & = & \expectation_{\Omega_l} [ I(p \geq M^{-1}) p^{-1} I(s \in S) ] \leq 1 \\
  \expectation_{\Omega_l} [ M + 1 - p^{-1} I(s \in S) ] & = & \expectation_{\Omega_l} [ I(p \geq M^{-1}) (M + 1 - p^{-1} I(s \in S)) ] \leq M  
\end{eqnarray*}
which implies $\expectation_{\Omega_l} [ p^{-1} I(s \in S) ] = 1$.
By linearity of expectation we can conclude that
\[
  \expectation_{\Omega_l} [ p^{-1} |\chi| ] = \sum_{s \in A} \expectation_{\Omega_l} [ p^{-1} I(s \in S) ] = |A| \textrm{.}
\]

>>>>

\section{Unbiasedness}
Let $M$ be large enough such that $p^{-1} \leq M$ a.s. (e.g. we can choose $M = f^{-l}$). Then we can derive from Lemma~\ref{le:neg_cor_neg} using $h(x) = x$ and $h(x) = M+1-x$ that:
\begin{eqnarray*}
  \expectation_{\Omega_l} [ p^{-1} I(s \in \chi) ] & = & \expectation_{\Omega_l} [ I(p \geq M^{-1}) p^{-1} I(s \in \chi) ] \leq 1 \\
  \expectation_{\Omega_l} [ M + 1 - p^{-1} I(s \in \chi) ] & = & \expectation_{\Omega_l} [ I(p \geq M^{-1}) (M + 1 - p^{-1} I(s \in \chi)) ] \leq M  
\end{eqnarray*}
which implies $\expectation_{\Omega_l} [ p^{-1} I(s \in \chi) ] = 1$.
By linearity of expectation we can conclude that
\[
  \expectation_{\Omega_l} [ p^{-1} |\chi| ] = \sum_{s \in A} \expectation_{\Omega_l} [ p^{-1} I(s \in \chi) ] = |A| \textrm{.}
\]

\section{Other approaches}
Initially I had tried to show that the RV's $I(s \in \chi)$ might be negatively associated. Unfortunately that is wrong, and because of the closure properties of
negative association the same is true of $p^{-1} I(s \in \chi)$.

The best counter-example (so far) I have is: 
\begin{itemize}
\item $a_1 = 1, \ldots, a_{15} = 15$ 
\item $n = 10$
\item $f = \frac{1}{2}$
\end{itemize}
then the RV's $f(\chi) = I(|\chi \cap \{1,..,10\}| \geq 5)$ and $g(\chi) = |\chi \cap \{11,\ldots,15\}|$ then 
\[
  E f g > E f E g
\]
with
\begin{eqnarray*}
  E f E g & = & \frac{59537}{24576} < 2.4225667318 \\
  E f g & = & \frac{78625}{32256} > 2.4375310019 
\end{eqnarray*}

Note: I verified this using Haskell with exact computation, i.e, we branch on every coin flip and big integer rational arithmetic. So these are exact values.
